---
title: Histograms
author: KImberly Staudt
date: '2017-10-08'
slug: histograms
categories: [R Studio]
tags: [dplyr, ggplot2,lahman,data visualization]
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the second tutorial on creating historgrams via RStudio.
Install the following and pull from the library:

```{r warning=FALSE, message=FALSE}
library(dplyr)
library(Lahman)
library(ggplot2)
```

##Extracting the Data

Assigned the extracted data to result (dataframe).
```{r warning=FALSE, message=FALSE}
result<-Batting%>%
        filter(playerID=='ruthba01')%>%
        select(yearID,SO,HR)
```

##Data visualization

In the last post, we used ggplot to create a visual representation of the data. In this representation, we are going to name our <i>x</i> and <i>y</i> coordinates with <i>xlab</i> and <i>ylab</i>, repsectively.  Use <i>ggiraph</i> to change color characteristics when hovering over the graph.
```{r warning=FALSE, message=FALSE}

ggplot()+
  geom_histogram(data=result,aes(x=HR),bins=5,color="red",fill="white")

```






