---
title: "Histograms 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the second tutorial on creating historgrams via RStudio.
Install the following and pull from the library:

```{r warning=FALSE, message=FALSE}
library(dplyr)
library(Lahman)
library(ggplot2)
library(ggiraph)
```

##Extracting the Data

In the last post, we assigned our extracted data to df(dataframe).Complete this step again.
```{r warning=FALSE, message=FALSE}
df<-Teams%>%
  filter(yearID==1980)%>%
  select(name,HR)%>%
  arrange(HR)
  
```

<b>str</b> give the structure of whatever data you have. Store your data as a factor vector, rather than a character vector.The benefit to this is that factor vectors are organized into different levels . 
Type <b>class(df$name)</b> to confirm that the data has been stored correctly. 
Use <b>levels(df$name)</b> to view levels.
Use <b>levels=df$name</b> to set levels to the same order as the columns. 

```{r warning=FALSE,message=FALSE}
str(df$name)  
df$name<-factor(df$name,levels=df$name) 
```


##Data visualization

In the last post, we used ggplot to create a visual representation of the data. In this representation, we are going to name our <b>x</b> and <b>y</b> coordinates with <b>xlab</b> and <b>ylab</b>, repsectively. 
```{r}
g<-ggplot()+
  geom_bar(data=df,aes(x=name,y=HR,tooltip=HR, data_id=name), stat="identity", color="blue",fill="white")+
  coord_flip()+
  ggtitle("1980 Team Homeruns")+
  xlab("Team")+
  ylab("Homeruns")
```

Optional: Use <b>ggiraph</b> to change color characteristics when hovering over the graph:

ggiraph(code=print(g), hover_css=fill:"red";stroke:"white")

