---
title: Word Clouds
author: Kimberly Staudt
date: '2017-11-01'
slug: how-to-create-a-word-cloud
categories: [R Studio]
tags: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidytext)
library(wordcloud)
```

##What is a Word Cloud?

A word cloud is an image composed of words whose size is determined by the frequency in which they appear. Today, we will be creating a word cloud from the Tame Impala album, Currents. First, create a word text file, and save the lyrics (no titles) in that file. 
Save both this file and a new R script file in the same directory. Now we can begin. 


Read in the text file with the <b>scan</b> function.Scanning the data shows that there are 407 lines. The character function returns the character value, while the new line is used as a seperator. Store the in the variable,<i>lines</i>.
```{r  warning=FALSE, message=FALSE}
lines<-scan('currents album.txt',what=character(),sep='\n')
```

Run head(lines) to view the the first several rows of the matrix/data frame. You can also use tail(lines) to view the last rows. 

Create a new data fram with that views each line of text. Earlier we saw that we had 407 lines. Set <i>line</i> equal to the ratio of the first to last line. Set text equal to  <i>lines</i>.
```{r  warning=FALSE, message=FALSE}
lines_df<-data_frame(line=1:407,text=lines)
```

Now, use unnest_tolkens() to create a new column, word, from text. Store this into the data frame, words_df
```{r warning=FALSE, message=FALSE}
words_df<-lines_df%>%
  unnest_tokens(word,text)
```

Common words can clutter our word cloud. Filter these out with <b> %in% </b>. This compares the word column in words dataframe to the word column in the stop_words dataframe. Use the ! symbol to stop common words. Store back into words_df.

```{r  warning=FALSE, message=FALSE}
words_df<-words_df%>%
  filter(!(word %in% stop_words$word))
```

Next,group by the word column. Use summarise to count the number of times the the appears. Store as word_freq.
```{r  warning=FALSE, message=FALSE}
word_freq<-words_df%>%
  group_by(word)%>%
  summarise(count=n())
```

We are now ready to finalize our wordcloud. View pallete colors with  the display.brewer.all() function. We are going to select the word and count column in word_freq. Our color pallete today is called Set2. 
```{r  warning=FALSE, message=FALSE}

wordcloud(word_freq$word,word_freq$count,color=brewer.pal(24, 'Set2'))
```

