---
title: Time Series
author: Kimberly Staudt
date: '2017-10-14'
slug: timeseries
categories: [R Studio]
tags: [dplyr,lahman, ggplot2]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a tutorial on how to create a time series plot in R Studio. We will be using the same data we used to create an instagram, and apply the same extracting techniques.

Install the following and pull from the library:

```{r warning=FALSE, message=FALSE}
library(dplyr)
library(Lahman)
library(ggplot2)
```

##Extracting the Data

Assigned the extracted data to result (dataframe).
```{r warning=FALSE, message=FALSE}
result<-Batting%>%
        filter(playerID=='ruthba01')%>%
        select(yearID,SO,HR)
```

##Data visualization

In this representation, we are going to name our <i>x</i> and <i>y</i> coordinates with <i>xlab</i> and <i>ylab</i>, repsectively. Use geom point to create the data points, and geom line to connect those points. 
```{r warning=FALSE, message=FALSE}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR),color="red",size=5)+
  geom_line(data=result,aes(x=yearID,y=HR), color="blue", size=3)+
  xlab("year")+
  ylab("homeruns")

```






